Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-27 sections/tensors.tex
cool
okay, I'm calling it
something like that
Update on Overleaf.
fix

\subsection{The 8 Key Level Structures}
    The main benefits of specializing to structure come from the following properties of the data:
    \begin{enumerate}
        \item[Sparsity] Sparse data is data that is mostly zero, or some other
        fill value. When we specialize on this data, we can use annihilation ($x
        * 0 = 0$), identity ($x * 1 = 1$), or other constant propagation
        properties ($ifelse(false, x, y) = y$) to simplify the computation and avoid
        redundant work.

@@

    In Finch, we have identified 8 key level structures that can represent all
    of the relevant combinations of these properties, summarized in Table
    \ref{tab:TypesOfStructure}. We examine each structure in turn, describing
    some of the key properties and potential use cases of each. In this sense,
    the structures we consider are exhaustive. We can represent a wide variety
    of hierarchical tensor structures by combining these level structures in a
    tree, as shown in Figure~\ref{fig:structuraldiversity}.
    \begin{table}
        \centering
        \begin{tabular}{|c|c|c|c|l|}
            \hline
            \textbf{Sparse} & \textbf{Blocked} & \textbf{Runs} & \textbf{Singletons} & \textbf{Corresponding Format} \\
            \hline
             &  &  &  & Dense \\
            \hline
             &  & \checkmark &  & DenseRLE \\
            \hline
            \checkmark &  &  &  & Sparse \\
            \hline
            \checkmark &  &  & \checkmark & SparsePinpoint \\
            \hline
            \checkmark &  & \checkmark &  & SparseRLE \\
            \hline
            \checkmark &  & \checkmark & \checkmark & SparseInterval \\
            \hline
            \checkmark & \checkmark &  &  & SparseVBL \\
            \hline
            \checkmark & \checkmark &  & \checkmark & SparseBand \\
            \hline
        \end{tabular}
        \caption{All combinations of relevant structural properties and their
        corresponding formats.  Note that blocks and runs need not be considered
        together because we must store a run length for each run, and so there
        isn't a significant storage benefit to combining them. Blocks and
        singletons only make sense in the contex of sparsity, so we don't
        consider them together either. We omit such combinations
        from the exhaustive table.}
        \label{tab:TypesOfStructure}
    \end{table}

@@

>>>>

\subsection{The 8 Key Level Structures}
    \begin{wrapfigure}{r}{.35\textwidth}
        \centering
        \scriptsize
        \begin{tabular}{|c|c|c|c|l|}
            \hline
            \rothead{Sparse} & \rothead{Blocked} & \rothead{Runs} & \rothead{Singletons} & \begin{tabular}{@{}l@{}}\textbf{Corresponding} \\ \textbf{Format}\end{tabular} \\
            \hline
             &  &  &  & Dense \\
            \hline
             &  & \checkmark &  & DenseRLE \\
            \hline
            \checkmark &  &  &  & Sparse \\
            \hline
            \checkmark &  &  & \checkmark & SparsePinpoint \\
            \hline
            \checkmark &  & \checkmark &  & SparseRLE \\
            \hline
            \checkmark &  & \checkmark & \checkmark & SparseInterval \\
            \hline
            \checkmark & \checkmark &  &  & SparseVBL \\
            \hline
            \checkmark & \checkmark &  & \checkmark & SparseBand \\
            \hline
        \end{tabular}
        \caption{All combinations of relevant structural properties and their
        corresponding formats.  Note that blocks and runs need not be considered
        together because we must store a run length for each run, and so there
        isn't a significant storage benefit to combining them. Blocks and
        singletons only make sense in the contex of sparsity, so we don't
        consider them together either. We omit such combinations
        from the exhaustive table.}
        \label{tab:TypesOfStructure}
    \end{wrapfigure}
    The main benefits of specializing to structure come from the following properties of the data:
    \begin{enumerate}
        \item[Sparsity] Sparse data is data that is mostly zero, or some other
        fill value. When we specialize on this data, we can use annihilation ($x
        * 0 = 0$), identity ($x * 1 = 1$), or other constant propagation
        properties ($ifelse(false, x, y) = y$) to simplify the computation and avoid
        redundant work.

@@

    In Finch, we have identified 8 key level structures that can represent all
    of the relevant combinations of these properties, summarized in Table
    \ref{tab:TypesOfStructure}. We examine each structure in turn, describing
    some of the key properties and potential use cases of each. In this sense,
    the structures we consider are exhaustive. We can represent a wide variety
    of hierarchical tensor structures by combining these level structures in a
    tree, as shown in Figure~\ref{fig:structuraldiversity}.

@@

\subsection{Scalars}

\subsubsection{Sparse Scalars}
\subsubsection{Early Break Scalars}
